A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-04-02 paper/sections/intro.tex
Adding NIST RBAC standard in Intro
why RBAC stand is initiated.

The RBAC standard was first introduced in the 1990s when the National Institute for Standards and Technology (NIST) 
requested that a unified standard be created by combining the Ferraiolo and Kuhn model \cite{ferraiolokuhn} with the framework 
proposed by Sandhu, et al \cite{sandhu1996role}.  In 2004, this standard was adopted as ANSI/INCITS 359-2004.  The development of a standard was inspired by an economic impact study done 
during the 1990s and later confirmed in 2011 \footnote{\url{http://csrc.nist.gov/groups/SNS/rbac/documents/20101219_RBAC2_Final_Report.pdf}}
that showed the cost savings of RBAC in implementation and maintenance.
RBAC is a generalized access control approach used for various applications including web services, 
database applications, and healthcare applications.  RBAC has advantages in maintaining and managing organization's security policies.  
For example, if a user is to access manager role's resources within a given organization, security policy administrators simply add the user to be associated with the manager role.
In an RBAC model, roles represent a group of users who are involved in a specific job function in an organization. RBAC assigns permissions 
of specific actions on resources to roles instead of individual users. Therefore, in order to gain a roles' permission on specific resources, 
users acquire appropriate roles first.

>>>>

The RBAC standard was first introduced in the 1990s when the National Institute for Standards and Technology (NIST) 
requested that a unified standard be created by combining the Ferraiolo and Kuhn model \cite{ferraiolokuhn} with the framework 
proposed by Sandhu, et al \cite{sandhu1996role}.  In 2004, this standard was adopted as ANSI/INCITS 359-2004 approved by American National Standards Institute (ANSI) and the InterNational Committee for Information Technology Standards (INCITS). INCITS is an international organization, which approves and maintains information technology standards. INCITS operates under rules approved by American National Standards Institute (ANSI). The development of a standard was inspired by an economic impact study done during the 1990s and later confirmed in 2011 \footnote{\url{http://csrc.nist.gov/groups/SNS/rbac/documents/20101219_RBAC2_Final_Report.pdf}}
that showed the cost savings of RBAC in implementation and maintenance.
More specifically, NIST initiated the development of RBAC standard because NIST found that IT developers and users in government and industry need consistent and uniform definition of RBAC features. In prior to the development of RBAC standard, vendors proposed and implemented their own defined RBAC features without general agreement on the unified definition of RBAC features. As a result, IT developers and users have uncertainty and confusion of RBAC features. Due to this uncertainty and confusion, not only development and maintenance cost of RBAC but also frequencies of security violations increase. RBAC standard address this issue by describing definition and functional specification of RBAC features using a reference model.

RBAC is a generalized access control approach used for various applications including web services, 
database applications, and healthcare applications.  RBAC has advantages in maintaining and managing organization's security policies.  
For example, if a user is to access manager role's resources within a given organization, security policy administrators simply add the user to be associated with the manager role.
In an RBAC model, roles represent a group of users who are involved in a specific job function in an organization. RBAC assigns permissions 
of specific actions on resources to roles instead of individual users. Therefore, in order to gain a roles' permission on specific resources, 
users acquire appropriate roles first.
